CALVIS: Chest, wAist and peLVIS circumference from 3D human body meshes as ground truth for deep learning

### 2019-09-27 PaperRMFI2019/samplepaper.tex
axilla recognition

The SMPL model is also a \textbf{deformable model} 
\cite{Terzopoulos:1987:EDM:37401.37427}. In order to 
synthesize a 
new human mesh one has to deform the provided template mesh by 
setting shape parameters $\vec{\beta}$. Pose parameters $\vec{\theta}$ are used 
for animation.

@@

@@

Let the axilla location be the point $p = (p^x, p^y, p^z)$ and 
$j_{nw}$, $j_{pl}$, 
$j_{lh} \in \mathbf{J}$ be the natural waist, pelvis and left hip joints, 
respectively.

@@

\begin{align}\label{eq:cr}
\mathcal{CR} = \big(v^y_i \, | \, p^y > v^y_i \geq j^y_{nw} \big)
\end{align}

\begin{align}\label{eq:wr}
\mathcal{WR} = \big(v^y_i \, | \, j^y_{nw} > v^y_i \geq j_{pl}\big)
\end{align}

\begin{align}\label{eq:pr}
\mathcal{PR} = \big(v^y_i \, | \, j_{pl} > v^y_i \geq j_{lh}\big)
\end{align}

\subsubsection{Axilla recognition}\label{subsec:armpit_recog}
As mentioned above, we would like to measure the chest circumference below the 
armpit, also known as axilla. This raises the question whether we can recognize 
the axilla. What we want is a point in the mesh at the proper location under 
the arms. One point suffices because we require only a reference along the 
y-axis to define the chest region according to equation \ref{eq:cr}. Therefore, 
we focus on the left shoulder joint $j_{ls} \in \mathbf{J}$. Since the axilla 
is related to 
the shoulder joint, we can cast a ray in direction $d$ outside the mesh. The 
joint $j_{ls}$ lies inside the mesh thus the ray intersects its surface at 
point $p$ (see 
figure x).

@@

@@

Note that for cross sections where $\boldsymbol{\pi_j}$ intersects the legs, 
two 
disconnected curves will appear. This is not necessarily a problem, because a 
set of disconnected curves has non-zero length (rf?).

>>>>

The SMPL model is also a \textbf{deformable model} 
\cite{Terzopoulos.1987}. In order to 
synthesize a 
new human mesh one has to deform the provided template mesh by 
setting shape parameters $\vec{\beta}$. Pose parameters $\vec{\theta}$ are used 
for animation.

@@

\begin{figure}[t]
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
		\includegraphics[width=\linewidth]{subjects_2_6_calvis_segmented.png}
	\end{center}
	\caption{Mesh segmentation in chest (red), waist (green) and pelvic (blue) 
	regions. We show male (left) and female (right) subjects in frontal and 
	lateral view.}
	\label{fig:axilla-recognition}
\end{figure}

@@

Let the axilla location be the point $p_a = (p^x_a, p^y_a, p^z_a)$ and 
$j_{nw}$, $j_{pl}$, 
$j_{lh} \in \mathbf{J}$ be the natural waist, pelvis and left hip joints, 
respectively.

@@

\begin{align}\label{eq:cr}
\mathcal{CR} = \big(v^y_i \, | \, p^y_a > v^y_i \geq j^y_{nw} \big)
\end{align}

\begin{align}\label{eq:wr}
\mathcal{WR} = \big(v^y_i \, | \, j^y_{nw} > v^y_i \geq j^y_{pl}\big)
\end{align}

\begin{align}\label{eq:pr}
\mathcal{PR} = \big(v^y_i \, | \, j^y_{pl} > v^y_i \geq j^y_{lh}\big)
\end{align}

\subsubsection{Axilla recognition}\label{subsec:armpit_recog}
As mentioned above, we would like to measure the chest circumference below the 
armpit, also known as axilla. This raises the question whether we can recognize 
the axilla. What we want is a point in the mesh at the proper location under 
the arms. One point suffices because we require only a reference along the 
y-axis to define the chest region according to equation \ref{eq:cr}. Therefore, 
we focus on the left shoulder joint $j_{ls} \in \mathbf{J}$. Since the axilla 
is related to 
the shoulder joint, we can cast a ray $\boldsymbol{\iota}$ from it in direction 
to the middle left 
inferior edge of the bounding box outside the mesh at point

\begin{align}
p_b = \bigg(v^x_{min}, v^y_{min}, v^z_{min} + 
\frac{v^z_{max} - v^z_{min}}{2}\bigg).
\end{align}

Here $v^x_{min}, v^y_{min}, v^z_{min}$ are vertex with minimum $x$,$y$ and $z$ 
coordinates, respectively. Distance $d(v^z_{max},v^z_{min})$ is the euclidean 
distance between vertices with maximum and minimum $z$ coordinate (figure x).

@@

\begin{figure}[H]
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
		\includegraphics[width=\linewidth]{axilla_recognition_final.png}
	\end{center}
	\caption{Axilla recognition based on the skeleton joint. We cast a ray from 
	the left shoulder joint in direction to the middle left 
		inferior edge of the bounding box (left). The ray intersects the mesh 
		at point $p_a$ that we consider the axilla center. We plot the 10 
		nearest vertices to $p_a$ (right). As it can be observed, the axilla is 
		properly recognized.}
	\label{fig:axilla-recognition}
\end{figure}

@@

Note that for cross sections where $\boldsymbol{\pi_j}$ intersects the legs, 
two 
disconnected curves will appear. This is not a problem, because a 
set of disconnected curves is, in our case, a collection of segments with 
non-zero length.
